Truth space method for caching database queries

### 2014-11-16 english_version/TODS/blind_review/blind_main.tex
Version for blind review was added.

\author{Mosin Sergey, Zykin Sergey}
\usepackage{amssymb,amsmath}
%\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage{xcolor}
%\usepackage{textcomp}
\newtheorem{note}{Note}
\newtheorem{statement}{Statement}
\def \eval #1#2{\left.#1\right\vert_{#2}}
\def \<#1> {\langle #1 \rangle}
\def \n #1{\mathit{#1}}

@@

% Page heads
\markboth{S.~V. Mosin, S.~V. Zykin}{Truth space method for caching database
queries}

% Title portion
\title{Truth space method for caching database queries}
\author{SERGEY V. MOSIN
\affil{Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences}
SERGEY V. ZYKIN
\affil{Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences}
}

@@

\category{C.2.2}{Computer-Communication Networks}{Network Protocols}

\terms{Caching, Optimization}

@@

\acmformat{Sergey V. Mosin and Sergey V. Zykin, 2014. Truth space method for
caching database queries}

\begin{bottomstuff}
This work is supported by the Russian Foundation for Basic Research under
grant \#12-07-00066-a.

Author's addresses: S.V. Mosin, Laboratory of information transformation and
representations methods, Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences; S.V. Zykin, Laboratory of information
transformation and representations methods, Sobolev Institute of Mathematics of
the Siberian Branch of the Russian Academy of Sciences.
\end{bottomstuff}

@@

In papers \cite{Keller96, shim} similar problem is discussed. In our paper we
make correspondence between cache contents and predicates. Cached data usage
problem is resolved in terms of truth spaces. We compute the truth spaces of
query results in the cache. It allows us to define records in IDV that can be
used to form a new view and new SQL queries that will let us load missing data
from Database server. The following example demonstrates suggested approach.

@@

% Electronic Appendix
\elecappendix

\medskip

\end{document}
% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

>>>>

\usepackage{amssymb,amsmath}
%\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage{xcolor}
%\usepackage{textcomp}
\newtheorem{note}{Note}
\newtheorem{statement}{Statement}
\def \eval #1#2{\left.#1\right\vert_{#2}}
\def \<#1> {\langle #1 \rangle}
\def \n #1{\mathit{#1}}

@@

% Title portion
\title{Truth space method for caching database queries}

@@

\category{H.2.3, H.2.4}{Database Management}{Languages, Systems}

\terms{Languages, Theory, Performance}

@@

@@

In papers \cite{Keller96}, \cite{shim} similar problem is discussed. In our
paper we
make correspondence between cache contents and predicates. Cached data usage
problem is resolved in terms of truth spaces. We compute the truth spaces of
query results in the cache. It allows us to define records in IDV that can be
used to form a new view and new SQL queries that will let us load missing data
from Database server. The following example demonstrates suggested approach.

@@

\end{document}
